Arbitrary Code Injection in Adblock Plus

### 2023-04-26 paper/paper.tex
Write

TODO: we make our project open source?

@@

% Author: Eric Li
The fifth comment is about Microsoft Edge. In our older draft of the paper we only mention Chrome (Chromium), Firefox, and Safari. We modify the paper to add Edge, since Edge is also a popular browser.

>>>>

To help future researchers reproduce this attack, our project is open source at https://github.com/lxylxy123456/14828. We try to make our work reproducible, such as by providing exact versions of software we use.

@@

% Author: Eric Li
The fifth comment is about Microsoft Edge. In our older draft of the paper we only mention Chrome (Chromium), Firefox, and Safari. We modify the paper to add Edge, since Edge is also a popular browser. We still assume the attack works on Edge with out actually testing, because as far as we know, Edge only works on Windows, but we are testing on Linux.
